Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-04 code/rmarkdown/article.Rmd
+ make file fix + article fix

First, we used multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456] to identify loci under selection. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. To avoid falsely classifying loci as adaptive, we grouped individuals into genetic lineages for each species (Figures S3--S28). We used the number of genetic lineages in each species previously identified by Alvarez _et al._ [-@r478]. Since \textit{`r missing.species`} was previously identified as containing only one population, it was not compatible with \texttt{BayeScan}. For each species, we used \texttt{Structure} [version 2.3.4; using same parameters as @r478 per run with `r structure.params.LST[[MODE]]$numruns` runs per species] and \texttt{ClumPP} [version 1.1.2; @r459] to group individuals into populations. We then ran $\texttt{Bayescan}$ for each species using these groupings [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456].  Additionally, we omitted individuals from this analysis when their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [$q \leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

>>>>

First, we used multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456] to identify loci under selection. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. To avoid falsely classifying loci as adaptive, we grouped individuals into genetic lineages for each species (Figures S3--S28). We used the number of genetic lineages in each species previously identified by Alvarez _et al._ [-@r478]. Since \textit{`r gsub('_', ' ' , missing.species, fixed=TRUE)`} was previously identified as containing only one population, it was not compatible with \texttt{BayeScan}. For each species, we used \texttt{Structure} [version 2.3.4; using same parameters as @r478 per run with `r structure.params.LST[[MODE]]$numruns` runs per species] and \texttt{ClumPP} [version 1.1.2; @r459] to group individuals into populations. We then ran $\texttt{Bayescan}$ for each species using these groupings [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456].  Additionally, we omitted individuals from this analysis when their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [$q \leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].
